Status of the open-source landscape for 3D CSEM modeling

### 2019-07-11 OpenSource-3D-CSEM.tex
Update reference PETGEM
Start emg3d-specific part

\begin{abstract} % 1-2 sentence(s) each
%
% (1) PRINCIPAL OBJECTIVES AND SCOPE OF THE WORK
%
% (2) METHODOLOGY
%
% (3) RESULTS
%
% (4) CONCLUSIONS
%
To-Do/-Discuss:
\begin{itemize}
  \item Title?
  \item Order of authors? These authors or others?
  \item Other codes to include? Currently considered:\\
    SimPEG, custEM, PETGEM, and emg3d.
  \item Are these references OK?
    \begin{itemize}
      \item \cite{CAG.15.Cockett} (SimPEG)
      \item \cite{GEO.18.Rochlitz} (custEM)
      \item \cite{CAG.18.CastilloReyes} (PETGEM)
      \item \cite{JOSS.19.Werthmuller} (emg3d).
    \end{itemize}
  \item Exact structure of the paper?
  \item Exact models to calculate/show/compare?
\end{itemize}
\end{abstract}

@@

Each code should outline:
\begin{itemize}
  \item Equation system it solves;
  \item the used discretization possibilities;
  \item domains (frequency, time);
  \item details (anisotropy; el. perm. and mag. perm.);
  \item other things (inversion; other methods);
  \item speed and memory estimation;
  \item plans for next features.
\end{itemize}

@@

@@

\section{Acknowledgment}
\dots

>>>>

\begin{abstract} % 1-2 sentence(s) each
%
% (1) PRINCIPAL OBJECTIVES AND SCOPE OF THE WORK
%
% (2) METHODOLOGY
%
% (3) RESULTS
%
% (4) CONCLUSIONS
%
To-Do/-Discuss:
\begin{itemize}
  \item Title?
  \item Order of authors? These authors or others?
  \item Other codes to include? Currently considered:\\
    SimPEG, custEM, PETGEM, and emg3d.
  \item Are these references OK?
    \begin{itemize}
      \item \cite{CAG.15.Cockett} (SimPEG)
      \item \cite{GEO.18.Rochlitz} (custEM)
      \item \cite{GJI.19.CastilloReyes} (PETGEM)
      \item \cite{JOSS.19.Werthmuller} (emg3d).
    \end{itemize}
  \item Exact structure of the paper?
  \item Exact models to calculate/show/compare?
\end{itemize}
\end{abstract}

@@

Each code should outline:
\begin{itemize}
  \item General presentation/introduction;
  \item Equation system it solves;
  \item the used discretization possibilities;
  \item domains (frequency, time);
  \item details (anisotropy; el. perm. and mag. perm.);
  \item other things (inversion; other methods);
  \item speed and memory estimation;
  \item plans for next features.
\end{itemize}

@@

\emph{General presentation/introduction}\\

\emph{Equation system it solves}\\

\emph{the used discretization possibilities}\\
The code requires regular, but not necessary equidistant, grids.

\emph{domains (frequency, time)}\\

\emph{details (anisotropy; el. perm. and mag. perm.)}\\
It currently includes tri-axial electric anisotropy and isotropic relative
magnetic permeability; the relative electric permittivity is fixed at 1.

\emph{other things (inversion; other methods)}\\

\emph{speed and memory estimation}\\
The advantage of multigrid methods is that they have optimal scaling for both
runtime and memory usage. If the number of cells is doubled it will take twice
as long and twice as much memory to calculate. Expand on that.

\emph{plans for next features}\\
According to the current roadmap the next step in the development of emg3d will
see routines for fast time-domain calculations with a frequency-domain code by
minimizing the required frequencies for the Fourier transform. Also planned are
the extension to general anisotropy, inversion routines, and some improved
routines for the inclusion of topography. Some of these might be sought to
achieve by a compatibility layer to SimPEG.

@@

\section{Acknowledgment}

The development of emg3d was funded through the European Commission: MarTERA -
Maritime and Marine Technologies for a New ERA (728053).
